Using Sorghum as an outgroup to find syntenic regions in Maize: regenerating

### 2017-08-18 R/SubGenome Analysis.Rmd
Tied GOSlim import to main report

```{r importSynMapData, include=FALSE}
source("~/git/SubGenomes/R/parseSubgenomes.R")
source("~/git/SubGenomes/R/addGOTerms.R")

@@

GO Terms by subgenome, only counting GO Terms that are in GOSlimPlant
```{r GOTerms_by_subgenome_goslim_import, echo=FALSE}
goSlim <- read_delim("../Data/goslim_plant.tab", "\t", escape_double = FALSE, trim_ws = TRUE)
# goSlim$GOSlimTerm <- paste("|",goSlim$GOSlimTerm,"|",sep = "")
```
```{r GOTerms_by_subgenome_goslim, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=4, fig.height=4}
# All EV-Codes, Unique GO Terms
grid.newpage()
g <- draw.pairwise.venn(
  area1 = goAnnotations.sub1 %>% inner_join(goSlim, by=c("GO Term" = "GOSlimTerm")) %>% select("GO Term") %>% distinct() %>% nrow(),
  area2 = goAnnotations.sub2 %>% inner_join(goSlim, by=c("GO Term" = "GOSlimTerm")) %>% select("GO Term") %>% distinct() %>% nrow(),
  cross.area = intersect(goAnnotations.sub1 %>% inner_join(goSlim, by=c("GO Term" = "GOSlimTerm")) %>% select("GO Term"), 
                         goAnnotations.sub2 %>% inner_join(goSlim, by=c("GO Term" = "GOSlimTerm")) %>% select("GO Term")) %>% 
              nrow(), 
  category = c("SubGenome 1", "SubGenome 2"), 
  lty = rep("blank", 2), 
  fill = c("light blue", "green"), 
  alpha = rep(0.5, 2), 
  cat.pos = c(0, 180), 
  scaled = FALSE,
  euler.d = FALSE, 
  sep.dist = 0.3, 
  rotation.degree = 0,
  ind = FALSE
)
grid.arrange(gTree(children=g), top="GO Term by Subgenome\n(All EV-Codes, GOSlim only)")

>>>>

```{r importSynMapData, include=FALSE}
source("~/git/SubGenomes/R/parseSubgenomes.R")
source("~/git/SubGenomes/R/addGOTerms.R")
source("~/git/SubGenomes/R/parseGOSlim.R")

@@

GO Terms by subgenome, only counting GO Terms that are in GOSlimPlant

```{r GOTerms_by_subgenome_goslim, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=4, fig.height=4}
# All EV-Codes, Unique GO Terms
grid.newpage()
g <- draw.pairwise.venn(
  area1 = goAnnotations.sub1 %>% inner_join(goSlim, by=c("GO Term" = "GOSlimTerm")) %>% select("GO Term") %>% distinct() %>% nrow(),
  area2 = goAnnotations.sub2 %>% inner_join(goSlim, by=c("GO Term" = "GOSlimTerm")) %>% select("GO Term") %>% distinct() %>% nrow(),
  cross.area = intersect(goAnnotations.sub1 %>% inner_join(goSlim, by=c("GO Term" = "GOSlimTerm")) %>% select("GO Term"), 
                         goAnnotations.sub2 %>% inner_join(goSlim, by=c("GO Term" = "GOSlimTerm")) %>% select("GO Term")) %>% 
              nrow(), 
  category = c("SubGenome 1", "SubGenome 2"), 
  lty = rep("blank", 2), 
  fill = c("light blue", "green"), 
  alpha = rep(0.5, 2), 
  cat.pos = c(0, 180), 
  scaled = FALSE,
  euler.d = FALSE, 
  sep.dist = 0.3, 
  rotation.degree = 0,
  ind = FALSE
)
grid.arrange(gTree(children=g), top="GO Term by Subgenome\n(All EV-Codes, GOSlim only)")
